The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
phrasing

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, including those stars that were entirely unobserved. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. Aside from the restriction on stars falling on the edge of a chip like this or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.

In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.

>>>>

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, including those stars that were entirely unobserved. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. \textcolor{red}{Aside from the restriction on stars falling on the edge of a chip}, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.

In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.
